---
title: "Assignment B2"
author: "Sophie van Lotringen|Jesse van Lier|Anouk Bor|Martijn Kok|Youri Hanegraaf"
date: "30 mei 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("ez") 
#install.packages("multcomp") 
#install.packages("emmeans") 
#install.packages("car") 
#install.packages("rstatix") 
#install.packages("lmer") 
#install.packages("lmerTest") 
#install.packages("afex") 
#install.packages("moments")
#install.packages("sm")
#install.packages("eatATA")
#install.packages("rstatix")
#install.packages("psych")
#install.packages("ltm")
#install.packages("dplyr")
#install.packages("haven")
#install.packages("ggpubr")
```

## Load packages
```{r}
library(dplyr)
library(haven)
library(ez) 
library("multcomp") 
library("emmeans") 
library("car") 
library("rstatix") 
library("lmer") 
library("lmerTest") 
library("afex") 
library(ggplot2)
library(moments)
library("ggpubr")
library("sm")
library("eatATA")
library("rstatix")
library("psych")
library("ltm")

```


## Set working directory
```{r}
setwd("C:(SETWDHERE!!!)")

study_1 <- read_sav("./Idea 1/Exp+Res+2022+Idea+1+-+consume+v+purchase_May+9,+2022_15.04.sav")
dataset2 <- read_sav("./Idea 2/Exp+Res+2022+Idea+2+-+premium+vs+private+label_May+9,+2022_15.03.sav")

```


## Clean data
```{r}
# Create factor variables. 

study_1$FL_14_DO_buy_togo[is.na(study_1$FL_14_DO_buy_togo)] <- 0
study_1$FL_14_DO_consumetogo[is.na(study_1$FL_14_DO_consumetogo)] <- 0
study_1$FL_14_DO_buyhome[is.na(study_1$FL_14_DO_buyhome)] <- 0
study_1$FL_14_DO_consumehome[is.na(study_1$FL_14_DO_consumehome)] <- 0

study_1$gender <- as.factor(study_1$gender)
levels(study_1$gender) <- list("Male" = 1, "Female" = 2, "Non-binary / third gender" = 3, "Prefer not to say" = 4)
study_1$Status <- as.factor(study_1$Status)
study_1$UserLanguage <- as.factor(study_1$UserLanguage)

# Remove preview from data

study_1 <- study_1[study_1$Status != 1, ]

```

## Get summary statistics 
```{r}

summary(study_1)

```


## Create Variables
```{r}

#buy vs. consume

study_1$buy_consume <- study_1$FL_14_DO_buy_togo + study_1$FL_14_DO_buyhome
study_1$buy_consume <- as.factor(study_1$buy_consume)
levels(study_1$buy_consume) <- list("buy"=1,"consume"=0) 

#one vs. many units
study_1$one_many <- study_1$FL_14_DO_buyhome + study_1$FL_14_DO_consumehome
study_1$one_many <- as.factor(study_1$one_many)
levels(study_1$one_many) <- list("many units"=1,"one unit"=0) 

#Create factors of all variables:
study_1$FL_14_DO_buy_togo <- as.factor(study_1$FL_14_DO_buy_togo)
study_1$FL_14_DO_consumetogo <- as.factor(study_1$FL_14_DO_consumetogo)
study_1$FL_14_DO_buyhome <- as.factor(study_1$FL_14_DO_buyhome)
study_1$FL_14_DO_consumehome <- as.factor(study_1$FL_14_DO_consumehome)

## Put all perceived ranks in one variable

study_1$rank <- rowSums(study_1[,c("rank_b_hm_1", "rank_b_tg_1", "rank_c_hm_1", "rank_c_tg_1")], na.rm=TRUE)


```


## Check assumptions for ANOVA
```{r}
# Normally distributed
ggdensity(study_1$rank, 
          main = "Distribution of the dependent variable",
          xlab = "Rank",)

skewness(study_1$rank, na.rm = TRUE)
shapiro.test(study_1$rank) #<0.05, so significantly different from normal distribution

# The data is not normally distributed

```


## Study 1: Will the below average effect be less strong for consumption than for purchases?
```{r}
#We have a 2x2 design: buy vs consume, one unit vs. many units. Unfortunately the data does not meet the assumption of a normal distribution, therefore we cannot use an ANOVA. Since no non-parametric alternatives to a 2x2 ANOVA exist, we will not look for interactions and use two Mann-Whitney-Wilcoxon tests, one for each independent variable. 

#First calculate means to see whether below average effect exists:

mean(study_1$rank_b_tg_1, na.rm = TRUE)
mean(study_1$rank_c_tg_1, na.rm = TRUE)
mean(study_1$rank_b_hm_1, na.rm = TRUE)
mean(study_1$rank_c_hm_1, na.rm = TRUE)

#All means are below <50, so below average effect exists. But is it significantly stronger/ weaker when bought in bulk or bought to consume immediately? 

#Mann-Whitney-Wilcoxon tests:

wilcox.test(rank ~ one_many, data=study_1)
wilcox.test(rank ~ buy_consume, data=study_1)

#We find a significant main effect of the one vs. many condition. We find no significant effect of buying vs. consuming on the below average effect

means <- c(mean(study_1$rank_b_tg_1, na.rm = TRUE), mean(study_1$rank_c_tg_1, na.rm = TRUE), mean(study_1$rank_b_hm_1, na.rm = TRUE), mean(study_1$rank_c_hm_1, na.rm = TRUE))

barplot(means, names= c("buy one unit", "consume one unit", "buy multiple units", "consume multiple units"))


#We find that the below average effect is less strong for goods that you buy in bulk (pack of coffee instead of one cup of coffee). 

```

## Study 2: Is the below average effect stronger for private label products than for their premium label equivalents?
## And does this affect people’s WTP compared to what they think the average person’s WTP is?

```{r}


dataset4ca_study2 <- dataset2 %>% 
  select(relative_rank_1, WTP_self, WTP_others)

cronbach.alpha(dataset4ca_study2)
```

```{r}
#Filter Dataset idea 2

#Compute WTP average
dataset2$WTP_average <- dataset2$WTP_others - dataset2$WTP_self

#Create seperate datasets for means (not of importance)
dataprivate <- dataset2 %>% select(ResponseId, relative_rank_1, WTP_self, WTP_others, Main_Block_DO_buy_private, WTP_average) %>% na.omit
datapremium <- dataset2 %>% select(ResponseId, relative_rank_1, WTP_self, WTP_others, Main_Block_DO_buy_premium, WTP_average) %>% na.omit

#Create groups for private and premium within the main dataset
dataset2$Main_Block_DO_buy_private[is.na(dataset2$Main_Block_DO_buy_private)] <- 2
dataset2$Main_Block_DO_buy_groups <- with(dataset2, factor(Main_Block_DO_buy_private, levels = 1:2,
                                                           labels = c("Private", "Premium")))
```

```{r}
#Mean analyses for observational purpose
mean(dataprivate$relative_rank_1)
mean(datapremium$relative_rank_1)
mean(dataprivate$WTP_self)
mean(dataprivate$WTP_others)
mean(datapremium$WTP_self)
mean(datapremium$WTP_others)
```

```{r}
#Normality test (observational through density plot). We observe that the distribution is non-normal.
ggdensity(dataset2$relative_rank_1,
          main = "Density",
          xlab = "Relative Rank")

ggdensity(dataset2$WTP_average,
          main = "Density",
          xlab = "WTP_average")

#Shapiro wilkinson test for normality (Both variables ar distributed non-normally)
shapiro.test(dataset2$relative_rank_1)
shapiro.test(dataset2$WTP_average)

#Levene's test for homoscedasticity (non-normal distributions)
leveneTest(relative_rank_1 ~ Main_Block_DO_buy_groups, data = dataset2)
leveneTest(WTP_average ~ Main_Block_DO_buy_groups, data = dataset2)

#We find that WTP suffers from heteroskedasticity

#Manova cannot be run due to a non-normal distribution. We therefore run a Wilcox test for the main effect since the WTP data suffers from heteroskedasticity.

wilcox.test(relative_rank_1 ~ Main_Block_DO_buy_groups, data=dataset2)

#We find that the main effect of private vs. premium is significant. 

```



#Scrap paper

```{r}
## ANCOVA


sm.ancova(x = study_1$buy_consume, y = study_1$rank, group = study_1$group)


## ANOVA

interaction_model <- kruskal.test(rank ~ buy_consume*one_many, data = study_1)

 
interaction.model <- aov(rank ~ buy_consume*one_many) 
Anova(interaction.model, type = 3)

## Create group indicators

study_1 <- dummiesToFactor(study_1, dummies = c("FL_14_DO_buy_togo", "FL_14_DO_consumetogo", "FL_14_DO_buyhome", "FL_14_DO_consumehome"), facVar = "group")



```
