---
title: "Assignment B2"
author: "Sophie van Lotringen"
date: "23 mei 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("ez") 
install.packages("multcomp") 
install.packages("emmeans") 
install.packages("car") 
install.packages("rstatix") 
install.packages("lmer") 
install.packages("lmerTest") 
install.packages("afex") 
install.packages("moments")
install.packages("sm")
install.packages("eatATA")
install.packages("rstatix")

```

## Load packages
```{r}
library(dplyr)
library(haven)
library(ez) 
library("multcomp") 
library("emmeans") 
library("car") 
library("rstatix") 
library("lmer") 
library("lmerTest") 
library("afex") 
library(ggplot2)
library(moments)
library("ggpubr")
library("sm")
library("eatATA")
library("rstatix")

```


## Set working directory
```{r}
setwd("C:/Users/sophi/OneDrive/Documenten/Marketing Analytics/Experimental Research/Assignment B2")

study_1 <- read_sav("./Idea 1/Exp+Res+2022+Idea+1+-+consume+v+purchase_May+9,+2022_15.04.sav")
study_2 <- read_sav("./Idea 2/Exp+Res+2022+Idea+2+-+premium+vs+private+label_May+9,+2022_15.03.sav")

```

## Create Variables
```{r}

summary(study_1)

## Create factors for each condition

study_1$FL_14_DO_buy_togo[is.na(study_1$FL_14_DO_buy_togo)] <- 0
study_1$FL_14_DO_consumetogo[is.na(study_1$FL_14_DO_consumetogo)] <- 0
study_1$FL_14_DO_buyhome[is.na(study_1$FL_14_DO_buyhome)] <- 0
study_1$FL_14_DO_consumehome[is.na(study_1$FL_14_DO_consumehome)] <- 0

#buy vs. consume

study_1$buy_consume <- study_1$FL_14_DO_buy_togo + study_1$FL_14_DO_buyhome
study_1$buy_consume <- as.factor(study_1$buy_consume)
levels(study_1$buy_consume) <- list("buy"=1,"consume"=0) 

#one vs. many units
study_1$one_many <- study_1$FL_14_DO_buyhome + study_1$FL_14_DO_consumehome
study_1$one_many <- as.factor(study_1$one_many)
levels(study_1$one_many) <- list("many units"=1,"one unit"=0) 

## Put all perceived ranks in one variable

study_1$rank <- rowSums(study_1[,c("rank_b_hm_1", "rank_b_tg_1", "rank_c_hm_1", "rank_c_tg_1")], na.rm=TRUE)


```


## Check assumptions for ANOVA
```{r}
# Normally distributed
ggdensity(study_1$rank, 
          main = "Distribution of the dependent variable",
          xlab = "Rank",)

skewness(study_1$rank, na.rm = TRUE)
shapiro.test(study_1$rank) #<0.05, so significantly different from normal distribution

# The data is not normally distributed

```


## Study 1: Will the below average effect be less strong for consumption than for purchases?
```{r}
#We have a 2x2 design: buy vs consume, one unit vs. many units. Unfortunately the data does not meet the assumption of a normal distribution, therefore we cannot use an ANCOVA. Since no non-parametric alternatives to an ANCOVA exist, we will not look for interactions and use two Mann-Whitney-Wilcoxon tests, one for each independent variable. 

#First calculate means to see whether below average effect exists:
mean(study_1$rank_b_tg_1, na.rm = TRUE)
mean(study_1$rank_c_tg_1, na.rm = TRUE)
mean(study_1$rank_b_hm_1, na.rm = TRUE)
mean(study_1$rank_c_hm_1, na.rm = TRUE)

#All means are below <50, so below average effect exists. But is it significantly stronger/ weaker when bought in bulk or bought to consume immediately? 

#Mann-Whitney-Wilcoxon tests:

wilcox.test(rank ~ one_many, data=study_1)
wilcox.test(rank ~ buy_consume, data=study_1)

#We find a significant main effect of the one vs. many condition. We find no significant effect of buying vs. consuming on the below average effect

means <- c(mean(study_1$rank_b_tg_1, na.rm = TRUE), mean(study_1$rank_c_tg_1, na.rm = TRUE), mean(study_1$rank_b_hm_1, na.rm = TRUE), mean(study_1$rank_c_hm_1, na.rm = TRUE))

barplot(means, names= c("buy one unit", "consume one unit", "buy multiple units", "consume multiple units"))


#We find that the below average effect is less strong for goods that you buy in bulk (pack of coffee instead of one cup of coffee). 

```

## Validity test
```{r}



```


## Study 2: Is the below average effect stronger for private label products than for their premium label equivalents?
## And does this affect people’s WTP compared to what they think the average person’s WTP is?
```{r}


```



```{r}


```



```{r}


```


```{r}


```


```{r}


```

#Scrap paper

```{r}
## ANCOVA


sm.ancova(x = study_1$buy_consume, y = study_1$rank, group = study_1$group)


## ANOVA

interaction_model <- kruskal.test(rank ~ buy_consume*one_many, data = study_1)

 
interaction.model <- aov(rank ~ buy_consume*one_many) 
Anova(interaction.model, type = 3)

## Create group indicators

study_1 <- dummiesToFactor(study_1, dummies = c("FL_14_DO_buy_togo", "FL_14_DO_consumetogo", "FL_14_DO_buyhome", "FL_14_DO_consumehome"), facVar = "group")



```